### 2024-01-27 tesis_Ashish/Chapter4/chapter4.tex
update 27 Jan

\begin{table}[h]
  \centering
  \caption[$\sigma_{vis}$ bunch variation uncertainty]{Bunch to bunch variation of PCC visible cross section. The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.}
\begin{tabular}{cccccc}
\textbf{Scan} & \textbf{Mean} & \textbf{STD} & \textbf{(STD/Mean) [\%]} \\
\hline
vdM1 & 953621.33 & 1334.83 & 0.14 \\
Img1 & 959386.63 & 559.37 & 0.058 \\
Img3 & 964376.43 & 2502.04 & 0.26 \\
Img4 & 960386.85 & 2936.50 & 0.31 \\
vdM2 & 960566.04 & 4320.81 & 0.45 \\
vdM3 & 964566.94 & 3928.54 & 0.41 \\
vdM4 & 962586.52 & 3943.24 & 0.41 \\
\end{tabular}
%\caption[Uncertainty due to bunch to bunch variation]{Bunch to bunch variation of PCC visible cross section. The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.} %from the standard deviation of the individual bunch-to-bunch uncertainty, averaged over all scans. The “bunch uncertainty” equals the spread divided by the square root of the number of bunches.}
\label{tab:sigmavis_btob_values}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
\hline
Normalization  & Length scale & -  \\
 & Orbit drift &  -  \\
 & x-y nonfactorization & - \\
 & Beam-beam deflection + Dynamic $\beta^{*}$  & - \\
 & Beam current calibration  & - \\
 & Ghost and satellite & - \\
 & Scan to scan variation & 0.3 \\
 & Bunch to bunch variation & 0.1 \\
 & Cross detector consistency  & 0.5 \\
 & Background subtraction  & 0.1 \\
Integration & Afterglow  &  0.3 \\
 & Cross detector stability & 0.3 \\
 & Linearity  & 0.4 \\
%Total &  &  1.08 \\
\end{tabular}
%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
\label{tab:systematic-uncertainty}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption[$\sigma_{vis}$ bunch variation uncertainty]{Bunch to bunch variation of PCC visible cross section. The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean. SEM is the standard error on the mean}
\begin{tabular}{cccccc}
\textbf{Scan} & \textbf{Mean} & \textbf{STD} & \textbf{(SEM/$\sigma_{vis}$) [\%]} \\
\hline
vdM1 & 953621.33 & 1334.83 & 0.14 \\
Img1 & 959386.63 & 559.37 & 0.058 \\
Img3 & 964376.43 & 2502.04 & 0.26 \\
Img4 & 960386.85 & 2936.50 & 0.31 \\
vdM2 & 960566.04 & 4320.81 & 0.45 \\
vdM3 & 964566.94 & 3928.54 & 0.41 \\
vdM4 & 962586.52 & 3943.24 & 0.41 \\
\end{tabular}
%\caption[Uncertainty due to bunch to bunch variation]{Bunch to bunch variation of PCC visible cross section. The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.} %from the standard deviation of the individual bunch-to-bunch uncertainty, averaged over all scans. The “bunch uncertainty” equals the spread divided by the square root of the number of bunches.}
\label{tab:sigmavis_btob_values}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
\hline
Normalization  & Length scale & 0.2  \\
 & Orbit drift &  0.1  \\
 & x-y nonfactorization & 2.0 \\
 & Beam-beam deflection + Dynamic $\beta^{*}$  & 0.2 \\
 & Beam current calibration  & 0.2 \\
 & Ghost and satellite & 0.1 \\
 & Scan to scan variation & 0.3 \\
 & Bunch to bunch variation & 0.1 \\
 & Cross detector consistency  & 0.5 \\
& Background subtraction  & 0.1 \\
\hline
Integration & Afterglow  &  0.3 \\
 & Cross detector stability & 0.3 \\
& Linearity  & 0.4 \\
\hline
Total &  &  2.2 \\
\end{tabular}
%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
\label{tab:systematic-uncertainty}
\end{table}

### 2024-01-27 tesis_Ashish/Chapter5/chapter5.tex
update 27 Jan 2024
update 27 Jan

For module evaluation, the steps include:
\begin{enumerate}
    \item Lumi sections with low statistics are removed based on total PCC.
    \item All barrel Layer-0 modules are sidestepped due to their vulnerability to dynamic inefficiency.
    \item An intial filtering removes modules with 7\% average deviation of the module weight from its mean (shown in Fig. \ref{fig:stab_deviation_2022}). %Subsequent adjustments tighten this criterion, illustrated by further refinements to 2\% and 0.8\% respectively.

    \item Module stability is reviewed using an iterative method. In the case of the 2022F dataset, we introduce additional criteria at 2\% and 0.8\%. For different data periods, the specific values used depend on how good the initial module list is.

@@

Table \ref{tab:bad_modules} presents a quantitative summary of malfunctioning or "bad" modules across various periods. BPIX Layer0 has 96 bad modules. As we progress through the various periods in 2022 (from F to D), there is a general trend of increasing bad modules, both for stability and linearity considerations. This suggests that as time progresses, the number of malfunctioning modules tends to grow. The highest number of bad modules for stability is observed in the 2022D period with 1653 bad modules. On the other hand, the 2022D period also has the highest for linearity with 1677 bad modules. The vdM fill has 1693 bad modules, which is slightly higher than those in the 2022D period for stability but slightly less for linearity. There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{pas_22}. % \cite{bril2023moduleveto}.

@@

\begin{itemize}
    \item \textbf{Pedestal}: Represents a consistent noise in the pixel cluster count.

@@

\newpage
Background estimations are obtained from the Random trigger datasets, processed in 50 LS blocks. The corrections, determined from these backgrounds, are subsequently applied to the zero-bias data. %Post-fitting residuals help in verifying the accuracy of the process.
While Type 1 residuals are minimal, Type 2 shows a slight deviation of around 0.2\%.

Comparable patterns are observed for 2022 periods E, F and G. During periods C and D, data was limited to the "AlCALumiPixelsEXPRESS" stream with an outdated module selection. Consequently, direct re-evaluation became unfeasible. As a solution, stored afterglow corrections, bolstered by a 1.008 factor from period E data, were applied.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
\caption[2022 PCC Inst. Luminosity]{%
  PCC instantaneous luminosity as a function of lumi section for entire 2022 year.

@@

\newpage
\section{Systematic uncertainties}

@@

\begin{table}[!htp]
  \centering
  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\begin{tabular}{cccc}
\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & $\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$ [\%] \\
\hline
vdM1 & 1065.09 & 2.89 & 0.1286 \\
Img1 & 1070.14 & 3.94 & 0.1746 \\
Img2 & 1075.38 & 2.35 & 0.1040 \\
vdM3 & 1083.58 & 3.70 & 0.1616 \\
vdM4 & 1080.37 & 2.09 & 0.0920 \\
\end{tabular}
\label{tab:my_label}
%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\end{table}

@@

>>>>

For module evaluation, the steps include:
\begin{enumerate}
    \item Lumi sections with low statistics are removed based on total PCC.
    \item All barrel Layer-0 modules are sidestepped due to their vulnerability to dynamic inefficiency.
    \item An intial filtering removes modules with 2\% average deviation of the module weight from its mean (shown in Fig. \ref{fig:stab_deviation_2022}). %Subsequent adjustments tighten this criterion, illustrated by further refinements to 2\% and 0.8\% respectively.

    \item Module stability is reviewed using an iterative method. In the case of the 2022F dataset, we introduce additional criteria of 0.8\%. For different data periods, the specific values used depend on how good the initial module list is.

@@

Table \ref{tab:bad_modules} presents a quantitative summary of malfunctioning or "bad" modules across various periods. BPIX Layer0 has 96 bad modules. As we progress through the various periods in 2022 (from F to D), there is a general trend of increasing bad modules, both for stability and linearity considerations. The total number of bad modules  added to the veto list grows in each period due to the sequential or iterative nature of the procedure where the veto list for each period starts with the veto from the previous period \cite{pas_22}.

This suggests that as time progresses, the number of malfunctioning modules tends to grow. The highest number of bad modules for stability is observed in the 2022D period with 1653 bad modules. On the other hand, the 2022D period also has the highest for linearity with 1677 bad modules. The vdM fill has 1693 bad modules, which is slightly higher than those in the 2022D period for stability but slightly less for linearity. There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{pas_22}. % \cite{bril2023moduleveto}.

@@

\begin{itemize}
    %\item \textbf{Pedestal}: Represents a consistent noise in the pixel cluster count.

@@

\newpage
Background estimations are obtained from the Random trigger datasets, processed in 50 LS blocks. The corrections, determined from these backgrounds, are subsequently applied to the zero-bias data. %Post-fitting residuals help in verifying the accuracy of the process.
While Type 1 residuals are minimal, Type 2 shows a slight deviation of around 0.2\% as shown in Fig. \ref{fig:period_bound_45}.

Comparable patterns are observed for 2022 periods E, F and G. During periods C and D, data was limited to the "AlCALumiPixelsEXPRESS" stream with an outdated module selection. Consequently, direct re-evaluation became unfeasible. As a solution, stored afterglow corrections evaluated in the CMS prompt calibration stage, corrected by a factor 1.008 from period E data, were applied.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
\caption[2022 PCC Inst. Luminosity]{%
  PCC instantaneous luminosity as a function of lumi section for entire 2022 year.

@@

\section{Systematic uncertainties}

@@

\begin{table}[!htp]
  \centering
  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section (as shown in Fig. \ref{fig:period_bound_99}). $N_b$ is the number of bunches in the vdM scan. SEM is the standard error on the mean.}
\begin{tabular}{cccc}
\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & (SEM/$\sigma_{vis}$) [\%] \\
\hline
vdM1 & 1065.09 & 2.89 & 0.1286 \\
Img1 & 1070.14 & 3.94 & 0.1746 \\
Img2 & 1075.38 & 2.35 & 0.1040 \\
vdM3 & 1083.58 & 3.70 & 0.1616 \\
vdM4 & 1080.37 & 2.09 & 0.0920 \\
\end{tabular}
\label{tab:my_label}
%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
\end{table}

%$\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$

@@

%\begin{figure}[H]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
%\caption[2022 PCC Type 1 Afterglow Residuals]{%                                                                                                                                                                             
 %PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F. The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.

%\begin{figure}[H]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
%\caption[2022 PCC Type 2 Afterglow Residuals]{%
 % Type 2 residual as a function of instantaneous luminosity for period 2022F. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
%}
%\label{fig:period_bound_45}
%\end{figure}
